S19: REU Research Document

### 2019-07-09 paper.tex
small addition

We need an efficient and compact way to represent the sundry features of a codebase and of identifying which features commonly appear together. The field of association rule mining is recognized for its ability to discover sets of items that co-occur with high prevalence without much previous information about the population or features \cite{AiEtAl2018}. Given that we are trying to associate a set of features for a codebase without any dependable knowledge about which features are most likely to be most common, association rule mining presents useful and powerful tools. There are several challenges that we encounter. First we have a large number of features, especially in comparison to the number of files in which those features are found, so our chosen algorithm must work with high dimensional data. Second, code bases are active documents; they are constantly changing and updating, and their features are constantly changing as well, so our algorithm must work with incremental data. Finally, many association rule mining algorithms are recursive, but the data structure used to compact and mine the key features can become so deep that a recursive algorithm can cause a stack overflow error, so our algorithm should be iterative. Therefore, we need an incremental, non-recrusive association rule miner that can efficiently analyze high dimensional data. In the following subsections, we begin by establishing the notation we will use for the rest of the paper; we discuss how we filter, aggregate, and update the database used with the association rule miner; we discuss the details of the algorithm we implemented and how we generate queries using the key features we association. Finally, we discuss how queries are selected and presented to the user.

@@

\subsubsection{Filtering, aggregating, and updating information}

>>>>

We need an efficient and compact way to represent the sundry features of a codebase and of identifying which features commonly appear together. The field of association rule mining is recognized for its ability to discover sets of items that co-occur with high prevalence without much previous information about the population or features \cite{AiEtAl2018}. Given that we are trying to associate a set of features for a codebase without any dependable knowledge about which features are most likely to be most common, association rule mining presents a useful and powerful tool. However, we still encounter are challenges. First we have a large number of features, especially in comparison to the number of files in which those features are found, so our chosen algorithm must work with high dimensional data. Second, code bases are active documents; as the project progress, files are added, modified, and deleted, and their features may be added, modified, and deleted as well. Thus our algorithm must work with incremental data. Finally, many association rule mining algorithms are recursive, but the data structure used to compact and mine the key features can become so deep that a recursive algorithm can cause a stack overflow error, so our algorithm should be iterative. Therefore, we need an incremental, non-recursive association rule miner that can efficiently analyze high dimensional data. In the following subsections, we begin by establishing the notation we will use for the rest of the paper; we discuss how we filter, aggregate, and update the database used with the association rule miner; we discuss the details of the algorithm we implemented and how we generate queries using the key features we associate. Finally, we discuss how queries are selected and presented to the user.

// Aren't the first and third challenges related? Should they be explained together?

Node-FPGrowth is a Node.js module implemented by Alexis Facques and accessible online through the npm registry. (citation) Explanation of fpgrowth here

@@

\subsubsection{Filtering, aggregating, and updating information}
Explanation of createData.py
